An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
edits to hosting section

\subsection{Hosting CloudCoder}
We recognize that ease of installation is a critical factor for
adoption of a new pedagogical
technology for busy
faculty who may only have a few minutes to evaluate a new system.  We
are committed to making the installation process as simple and painless as 
possible.

Thus far each institution that has adopted CloudCoder has
provided a Linux server that we configured for them.  This has made
adoption very easy, but is unlikely to scale up as we acquire more
users.  We have asked Amazon for Amazon Web Services credits to
provide CloudCoder ``in the cloud'' to adopting institutions, and we
hope to add support for Google App Engine this summer.  Ease of
adoption is critical for CloudCoder.

>>>>

\subsection{Hosting CloudCoder}

We recognize that ease of installation is a critical factor for
adoption of a new pedagogical technology for busy
faculty who may only have a few minutes to evaluate a new system.  We
are committed to making the installation process as simple and painless as 
possible.

Setting up a CloudCoder instance requires two Linux servers: one to
host the web application and database, and another to build and
test the student submissions.  The installation process is reasonably well
automated, and can be completed by someone comfortable with
running Linux commands on remote servers in about an hour.
We have received one report of a user successfully installing CloudCoder
without assistance.  However, self-hosting is still a significant
barrier to adoption, and we are investigating ways to make it
easier for potential users to adopt CloudCoder.

To date, each institution that has adopted CloudCoder in production has
provided Linux servers that we configured for them.  This has made
adoption very easy, but is not a model that is likely to scale well
to larger numbers of institutions.  We recently received a grant
from Amazon of credits for Amazon Web Services\cite{aws},
which we plan to use to directly host CloudCoder for interested
institutions.  We are also investigating easier ways for
users to self-host, such as enabling CloudCoder to run on
hosting services such as Google App Engine\cite{gae}.
%  We have asked Amazon for Amazon Web Services credits to
%provide CloudCoder ``in the cloud'' to adopting institutions, and we
%hope to add support for Google App Engine this summer.  Ease of
%adoption is critical for CloudCoder.
